Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
Updated

\subsection{Normalized Importance Sampling}\label{sec:prac}
As mentioned in Section~\ref{sec:stopping}, importance weights are an additional source of variance. A standard way to cope with this issue is self-normalization \citep{precup2000eligibility}.
This technique can reduce the variance of the importance weights at the cost of introducing some bias. Whether the trade-off is advantageous depends on the specific task.  
Introducing self-normalization in the context of our algorithm, we switch from Eq.~\eqref{E:svrpg.estimate.batch} to:
\begin{align*}
\blacktriangledown J(\vtheta_{t}) = \wh{\nabla}_N J(\wt{\vtheta})
 + \frac{1}{B} \sum_{i=0}^{B-1} \left[
g(\tau_i|\vtheta_t)\right]\\ 
- \frac{1}{ \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
In Section \ref{sec:exp} we show that self-normalization can provide a performance improvement.

>>>>

\subsection{Normalized Importance Sampling}\label{sec:prac}
As mentioned in Section~\ref{sec:stopping}, importance weights are an additional source of variance. A standard way to cope with this issue is self-normalization~\citep[\eg][]{precup2000eligibility,owenmcbook}.
This technique can reduce the variance of the importance weights at the cost of introducing some bias~\citep[][Chapter 9]{owenmcbook}.
Whether the trade-off is advantageous depends on the specific task.  
Introducing self-normalization in the context of our algorithm, we switch from Eq.~\eqref{E:svrpg.estimate.batch} to:
\begin{align*}
        \blacktriangledown J(\vtheta_{t}) &= \wh{\nabla}_N J(\wt{\vtheta}) + \frac{1}{B} \sum_{i=0}^{B-1} \left[g(\tau_i|\vtheta_t)\right]\\ 
                                          &\qquad{} - \frac{1}{\Omega} \sum_{i=0}^{B-1} \left[ \omega(\tau_i|\vtheta_t, \wt{\vtheta}) g(\tau_i|\wt{\vtheta})
\right].
\end{align*}
where $\Omega = \sum_{i=0}^{B-1}\omega(\tau_i|\vtheta_t, \wt{\vtheta})$.
In Section \ref{sec:exp} we show that self-normalization can provide a performance improvement.
